Pillar 2 - Topic Modeling

### 2019-01-24 Pillar 2 - Topic Modeling.Rmd

  dataset   <- get(paste("d", level, "cast", sep = "_"))
  LDA_model <- LDA(
    x = dataset,
    k = n_topics,
    method = "Gibbs",
    control = list(
      nstart = 10,
      seed = c(1:10),
      best = TRUE,
      burnin = 4000,
      iter = 2000,
      thin = 500))
  nam <- paste("LDA", level, n_topics, sep = "_")

>>>>

  dataset   <- get(paste("d", level, "cast", sep = "_"))

  LDA_model <- LDA(
    x       = dataset,
    k       = n_topics,
    method  = "Gibbs",
    control = list(
      nstart  = 10,
      seed    = c(1:10),
      best    = TRUE,

      burnin  = 4000,
      iter    = 5000,
      thin    = 500,

      verbose = 1e3,
      save    = 1e3,
      keep    = 1e3)
    )

  nam <- paste("LDA", level, n_topics, sep = "_")
